---
title: "AM_Sep7_HomeRangeIndoor"
author: "Hector Marina"
date: "2023-09-04"
output: html_document
---

##C:\Users\user\Documents\\2 - Uppsala\\02-Analyses\\04-MayasManuscript\\08-script_areacovered_propensityscore2.R ##C:\Users\hrna0001\\Documents\\2 - Uppsala\\02-Analyses\\04-MayasManuscript\\00-functions\functions\_PA.R \<- This should work as is the last used.

# Home range methods on indoor data

Introduction about the script. Different parts:

### Required packages and functions

```{r pressure, echo=FALSE}
library()
source("scripts/Sep.../.HomeRange_functions.R")
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Reading farm information

Read cow information

```{r}

CPheno <- read.table("data/raw/indoor/Cow_Phenotypes.csv", header = TRUE, sep = ",")

```

Total number of individuals/lines in the phenotype information:
```{r}

nrow(CPheno)

```


Plotting the distribution of the data:
```{r}

hist(as.factor(CPheno$Parity))
hist(CPheno$Claw_health)

```

Plot information and stats.

```{r pressure, echo=FALSE}

plot(pressure)

```

Read map of the farm and plot the different areas.

```{r pressure, echo=FALSE}

  Dutch_Areas   <- read.csv("data/raw/areas_dutch.csv", header=FALSE)
  colnames(Dutch_Areas)<- c("X1","X2","Y1","Y2","Area")
  X_png<-max(Dutch_Areas$X2)
  Y_png<-max(Dutch_Areas$Y2)
  
  # Loading blue prints
  Dutch_r <- png::readPNG('data/processed/DutchBarnMap_blueprint_Areas2.png')
  Dutch_rg <- grid::rasterGrob(Dutch_r, width=unit(1,"npc"), height=unit(1,"npc"))
  
  Following: SocialNetworkAnalyses_Dutch/scripts/00-tests/00-Plotting_RTLScontacts.R

```

## Reading FA interpolated data

Read FA data + Explanation different interpolation methods

```{r pressure, echo=FALSE}

read data()
EarlyLactationGroup_idList.txt
FA_EarlyLactationGroup_20201017.zip
FA_EarlyLactationGroup_20201017_interpolated.zip
colnames(FAdataFile)<- c("FILE","id","tag","t1","x","y","z")


```

filter the animals that have information

```{r pressure, echo=FALSE}


Filtering data()


```

Contact plots

```{r pressure, echo=FALSE}


plots()


```

## Estimate indoor Home ranges

Estimate the home range of a targeted individual.

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Including Plots

Explanation of the subsection.

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Including Plots

Explanation of the subsection.

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Including Plots

Explanation of the subsection.

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

## Including Plots

Explanation of the subsection.

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
