---
title: "AM_Sep11_TimeBudgetIndoor"
author: "Keni Ren"
date: "2025-08-29"
output: html_document
---
## Introduction
In this session, we play with dairy cattle's time budget in a free-stall barn.
First, let us explain the FA, PC, PA, and PAA data.
Then, we will plot an individual's activity data and trajectory.
We could select a group of cows and calculate their daily time budget.
At last, we investigate if parity could affect cubicle occupancy.

## Structure of the code
- Example code: 'AM_Sep11_TimeBudgetIndoor.rmd'
- './TimeBudget_Functions/data.R':Functions to read, clean and manipulate data 
- './TimeBudget_Functions/plot.R':Functions to plot data
- './TimeBudget_Functions/analysis.R': Methods to process and analyse data 


```{r setup, include=FALSE}
#init

dataFolder <- "../../data/raw/indoor"
outputFolder<- "./Output"

source("./TimeBudget_Functions/plot.R")
source("./TimeBudget_Functions/data.R")
source("./TimeBudget_Functions/analysis.R")


```
## Activity data and trajectory
Here, we read in the barn's blueprint from .csv file, add function areas and bed number to the barn's blue print.Please check more in plot.R. 
  
```{r map}
barn<-readBarnData(paste0(dataFolder, "/BarnMap.csv"))
plotBarn(barn, bRotated = FALSE, axes = FALSE)
addBarnFeatures(barn)
```

Read in PA data, plot one individual's activity data and trajectory. Please read more in data.R.

```{r PA}

PAdata <- read.PAData(paste0(dataFolder,"/PA_20201017T000000UTC.csv"))
head(PAdata,8) #show first 8 rows of the data

```

```{r activity}
# Plot one individual's activity data
#pdf(paste0(outputFolder, "/PA.pdf"), width = 11, height = 6) #if you want to print it in PDF

id<-2421861

data <- PAdata[which(PAdata$id == id), ]
plotBarn(barn, bRotated = FALSE, axes = FALSE)
addBarnFeatures(barn)

points(data$x, data$y, pch = 19, col = data$activity + 1, cex = 0.5)


legend("bottomright", legend = c("Unknown", "Standing", "Walking", "In cubicle", 
                                 "At feed", "At drinker", "Out def", "Outside"), 
       title = "Activity", col = c(0, 1, 2, 3, 4, 5, 998, 999) + 1, pch = 19, bg = NA)

#dev.off() #if you want to print it in PDF

```

```{r trajcatory}
# Create PDF, plot one individual's trajcatory during specific time.

#pdf(paste0(outputFolder, "/traj.pdf"), width = 11, height = 6) #if you want to print it in PDF
plotPATrajectory(PAdata, id,
                 startTime = as.POSIXct("2020-10-17 14:15:00 CET"),
                 endTime = as.POSIXct("2020-10-17 16:00:00 CET"))
#dev.off()  #if you want to print it in PDF

```
## Daily time budget
We could select a group of cows and calculate their daily time budget.We define the time budget here as the the proportion of the daily activity that was spent in the Alley standing (1), Alley walking (2), cubicles (3) and feeding (4) area. Please check more in analysis.R.

```{r select}
#Select a group of cows
CPheno <- read.table(paste0(dataFolder,"/Cow_Phenotypes.csv"), header = TRUE, sep = ",")
Select <- CPheno[which(CPheno$Lactation_stage == "Early"&CPheno$Parity == "2"), ]
SelectTags <- Select$Tag
print(paste("Number of individuals: ", length(SelectTags)) )
print(SelectTags )

```

```{r timebudget}
#Timebudget
TBS=getTimeBudget(PAdata, selectedIDs=SelectTags)
print(TBS)
```
## Cubicle preference
Modern dairy cattle farms are usually equipped with cubicle systems to provide cows with comfortable conditions for lying down and resting. Cows are free to choose any cubicle they want, but in reality, they do not distribute themselves uniformly throughout the barn. There are many factors that affect where a cow lies down, such as hierarchy of a cow, access to resources, cow traffic nearby, etc. We could use real-time location system data to examine patterns of cubicle occupancy in relation to parity and lactation stage. Please check more in analysis.R.


Further read: [Churakov, Mikhail, et al. "Parity and days in milk affect cubicle occupancy in dairy cows." Applied Animal Behaviour Science 244 (2021): 105494.](https://www.sciencedirect.com/science/article/pii/S0168159121002811)


```{r cubicle, warning = FALSE, message = FALSE}

#Cubic usage heatmap

#pdf(paste0(outputFolder, "/CubicUsage.pdf"), width = 11, height = 6) #if you want to print it in PDF
CubicUsage=getDailyCubicleUsageHeatmap(PAdata,SelectTags,barn)
#dev.off()  #if you want to print it in PDF

```