---
title: "Animal Movement - Intro Exercise"
date: "2025-08-29"
output: html_document
---

*Hej Hej* !

Welcome to the Animal Movement - PhD course. We have prepared some exercises that will help you to:

-   Verify you have installed all the packages that we need during the course\
-   Get familiar with the GitHub content\
-   Run simple descriptive statistics on the course data

To run this script correctly, we recommend that you open the script (*AM_IntroExercise.Rmd*) from R-Studio. This will allow you to modify the contents of the script in the various command boxes and save the changes and results. We have estimated a preparation time of 1-2 hours.

Let's get to work! ;-)

## Package installation

We have prepared a script to help you install all the packages we need during the course. This script will first check that you have the correct version of R installed, and then proceed to install the required R packages, if they were not already installed. First, let's see how it works:\
\
1. Check if a package is already installed

```{r eval=FALSE}
requireNamespace("ggplot2")==TRUE
```

\
2. Install the package if it was not already installed

```{r eval=FALSE}
install.packages("ggplot2")
```

\
3. Check if the installation was performed correctly

```{r eval=FALSE}
requireNamespace("ggplot2")==TRUE
```

\
\
Now you can execute the package installation script:

```{r eval=FALSE}
source(".installpackages.R")
```

```         
Note: If you have not opened the document as instructed, you may need to change the command path.
The installation script is in this directory: ./scripts/sep4_session2_afternoon/.installpackages.R 
```

## Descriptive statistics exercises

The following two exercises will familiarise you with the data we will be using during the course.

### Exercise 1: Outdoor data

#### Step 1: Read in the outdoor data file

Read the file `./data/raw/outdoor/gpsdata_april_june2021.csv`.

```{r}
# Write here your code
```

\

#### Step 2: Number of individuals

Now, summarise how many individuals this file contains.

```{r}
# Write your code here
```

\

#### Step 3: Simple plots

Please choose one of the individuals and plot the location of this individual during the study period.

```{r}
# Write your code here
```

\

### Exercise 2: Indoor data

#### Step 1: Read in the indoor data file

Read the file `./data/raw/indoor/FA_EarlyLactationGroup_20201017.txt`.

```{r}
# Write your code here
```

\

#### Step 2: Number of data points per individual

Select one of the individuals from the individual list file (`./data/raw/indoor/EarlyLactationGroup_idList.txt`) and summarise the number of data points of this individual contained in the position data file.

```{r}
# Write your code here
```

\

#### Step 3: Simple plots

Please read the file (`./data/raw/indoor/Cow_Phenotypes.txt`), where you can find the cow's phenotype information. Plot the position of all cows in parity 2 during the period 11:00-11:59.

```{r}
# Write your code here
```

\
 

```         
Note: When you have finished the exercise, save your changes. Remember not to "Pull" once you have changed the files, or they will overwrite the original repository contents. If you want to make sure this doesn't happen, copy the file out of the directory.  
Any questions that arise will be answered on the first day of the course after we have presented the data we will be using during the week. This exercise has many possible solutions, we will upload one of them to the repository on the first day. 
```
